\fancyfoot[R]{NH}
\section*{Executive Summary}
\stepcounter{section}
\addcontentsline{toc}{section}{\numberline{\roman{section}}Executive Summary}
The aim of the PC-Based Modular Diagnostics Tool project is to design and implement
a low-cost, multi-purpose electronic diagnostics tool suitable for field and/or
hobbyist use. The tool should replace bulky, single-purposes tools such as the digital 
multimeter, waveform oscilloscope and logic analyzer by utilizing the processing
power of end-user's home personal computer.

This design report contains the necessary information to review the PC-Based Modular 
Diagnostics Tool project and consider it for implementation. Major sections of the
report include an introduction to the project, an overall project description,
total cost details, an implementation schedule and detailed technical descriptions of each
subsystem. Included in the subsystem descriptions are a description of each subsystem
and its relation to other subsystems, a summary of design options considered, a list 
of materials and components utilized, a summary of costs incurred and engineering drawings.

The total expected time to implement the design is 6 weeks. This estimate includes the 
further testing and design refinement, total time needed for order and fabrication of parts, 
subsequent assembly of parts and final product testing.

The total cost for implementation of the PC-Based Modular Diagnostics Tool is \$191.87. For a more detailed breakdown of the cost please refer to Table \ref{tab:cost_est}.
